---
title: "Pilot analysis"
author: "Jae Yeon Kim, Joan Cho, Taeku Lee, DG Kim"
date: "`r Sys.Date()`"
output:
  #bookdown::html_document2:
  bookdown::pdf_document2:
    fig_caption: yes
    latex_engine: xelatex
    number_sections: true
    toc: yes
    toc_depth: 2
editor_options:
  chunk_output_type: console
link-citations: yes
linkcolor: blue
subparagraph: yes
citecolor: blue
urlcolor: blue
#header-includes:
---

# Pilot survey backgrounds 

* [Qualtrics survey link](https://jh.qualtrics.com/jfe/form/SV_0PXTsd1Ueux8aiO)
* Survey firm: [Savanta](https://savanta.com/us/) (founded in 2019)
* Sampling method: Quota sampling
* Survey target: This survey includes 1,000 Asian respondents in the United States, including those who were born in the US, as well as Chinese Americans and others.
* Actual sample size: 1,006 
* Survey period: July 12-July 20, 2023 (`r difftime("2023-07-20", "2023-07-12", units = c("days"))` days)

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)

if (!require(pacman)) install.packages("pacman")

pacman::p_load(tidyverse, here, readxl, estimatr, modelsummary, effectsize, broom, markdown,
               survey,  # weighted proportion tables
               anesrake) # creating weight variables

df <- read_xlsx(here("raw_data", "pilot_data_raw.xlsx"), skip = 1)
```

```{r reshape data, include = FALSE}
# remove survey distribution related variables
df <- df[, 18:ncol(df)]

df <- df[, -c((ncol(df) - 6):ncol(df))]

org_questions <- names(df)
```

```{r recode data, include = FALSE}
names(df) <- c(
  "age", "gender", "gender_other", "race_id", "born_us",
  "party_id", "strong_dem_id", "strong_gop_id", "leaning_party_id", # q1-9

  "china_virus_racist", "violence_against_asians", # q10-11
  "discrimination_happened_covid", # q12

  "democracy_importance", # q13
  "pol_strong_leader", "pol_democratic", "pol_army_rule", # q14-16

  "attention_check", # q17

  "asian_id", "asian_id_other", "asian_id_importance", # q18-20

  "ethnic_linked_fate", "racial_linked_fate", "asian_interests", # q21-23

  "national_attachment", "american_id_importance", # q24-25

  "china_fav", "china_threat", "china_demo"
) # q26-28

# demographic variables
df$age <- (df$age + 17)
df$female <- ifelse(df$gender == 2, 1, 0)
df$us_born_cat <- ifelse(df$born_us == 2, 1, 0)

# China virus statement
df$china_virus_racist[df$china_virus_racist == 31] <- 5
df$china_virus_racist[df$china_virus_racist == 32] <- 4
df$china_virus_racist[df$china_virus_racist == 33] <- 3
df$china_virus_racist[df$china_virus_racist == 34] <- 2
df$china_virus_racist[df$china_virus_racist == 35] <- 1

# Democrat ID dummy
df$dem <- ifelse(df$party_id == 1, 1, 0)

df$gop <- ifelse(df$party_id == 2, 1, 0)

# Violence against Asians
df <- df %>%
  mutate(violence_asian_cat = recode(violence_against_asians,
    `1` = "3",
    `2` = "1",
    `3` = "2"
  )) %>%
  mutate(violence_asian_cat = as.numeric(violence_asian_cat))

# Experiencing racial discrimination

df$racial_covid_dis_cat <- ifelse(df$discrimination_happened_covid != "11", 1, 0)

# national origin dummies
df$chinese <- ifelse(df$asian_id == 1, 1, 0)
df$filipino <- ifelse(df$asian_id == 2, 1, 0)
df$indian <- ifelse(df$asian_id == 3, 1, 0)
df$japanese <- ifelse(df$asian_id == 4, 1, 0)
df$korean <- ifelse(df$asian_id == 5, 1, 0)
df$other_nat <- ifelse(df$asian_id == 6, 1, 0)

df <- df %>%
  mutate(ethnic_linked_fate = recode(ethnic_linked_fate,
    `1` = "5",
    `8` = "4",
    `9` = "3",
    `10` = "2",
    `11` = "1"
  )) %>%
  mutate(ethnic_linked_fate = as.numeric(ethnic_linked_fate))

df$asian_id_importance[df$asian_id_importance == 16] <- 5
df$asian_id_importance[df$asian_id_importance == 17] <- 4
df$asian_id_importance[df$asian_id_importance == 18] <- 3
df$asian_id_importance[df$asian_id_importance == 19] <- 2
df$asian_id_importance[df$asian_id_importance == 20] <- 1

df$racial_linked_fate <- (6 - df$racial_linked_fate)

df$asian_interests[df$asian_interests == 21] <- 5
df$asian_interests[df$asian_interests == 22] <- 4
df$asian_interests[df$asian_interests == 23] <- 3
df$asian_interests[df$asian_interests == 24] <- 2
df$asian_interests[df$asian_interests == 25] <- 1

df$asian_interests <- (6 - df$asian_interests)

df$national_attachment <- (5 - df$national_attachment)

df$pol_strong_leader <- (5 - df$pol_strong_leader)

df$pol_democratic <- (5 - df$pol_democratic)

df$pol_army_rule <- (5 - df$pol_army_rule)

df <- df %>%
  mutate(asian_nat = case_when(
    asian_id == 1 ~ "Chinese",
    asian_id == 2 ~ "Flipino",
    asian_id == 3 ~ "Indian",
    asian_id == 4 ~ "Japanese",
    asian_id == 5 ~ "Korean",
    asian_id == 6 ~ "Others"
  ))
```


```{r include=FALSE}
# 2020 estimates from the US Census
# Chinese - 24%
# Indian - 21%
# Foreign born rate - 60%
# Female - 53%

df_unweighted <- svydesign(
    id = ~1, 
    data = df
)

# population-level distributions 
chinese_dist <- data.frame(chinese = c(1, 0),
                           Freq = nrow(df) * c(0.24, 0.76))

indian_dist <- data.frame(indian = c(1, 0),
                          Freq = nrow(df) * c(0.21, 0.79))

usborn_dist <- data.frame(us_born_cat = c(1, 0),
                          Freq = nrow(df) * c(0.4, 0.6))

female_dist <- data.frame(female = c(1, 0),
                          Freq = nrow(df) * c(0.53, 1-0.53))

# raking 
df_raked <- rake(design = df_unweighted,
                 sample.margins = list(~chinese, ~indian, ~female, ~us_born_cat),
                 population.margins = list(chinese_dist, indian_dist, female_dist, usborn_dist))

# summarize weights 
summary(weights(df_raked))

# add weights 
df$weights <- weights(df_raked)
```

# Summary statistics

Table \@ref(tab:sum-table) describes the demographic and political backgrounds of the survey respondents. With the exception of the age variable, all variables are dummy variables (1 = "yes", 0 = "no").

```{r, include=FALSE, message=FALSE, warning=FALSE}
sum_table <- df %>%
  select(age, female, us_born_cat, gop, dem, chinese, filipino, indian, japanese, korean, other_nat)

names(sum_table) <- c("Age", "Female", "US born", "GOP", "DEM", "Chinese", "Filipino", "Indian", "Japanese", "Korean", "Other national origins")
```

```{r sum-table, echo = FALSE}
datasummary_skim(sum_table,
  histogram = FALSE,
  title = "Summary table",
  fmt = 2
)
```

\newpage

```{r, include = FALSE}
cm <- c(
  "violence_asian_cat" = "Violence increased against Asians during COVID",
  "racial_covid_dis_cat" = "Experienced racial discrimination during COVID",
  "democracy_importance" = "Democracy importance",
  "pol_strong_leader" = "Strong leader favorability",
  "pol_democratic" = "Democratic system favorability",
  "pol_army_rule" = "Army rule favorability",
  "china_fav" = "China favorability",
  "china_threat" = "China threatening",
  "china_demo" = "China democratic",
  "american_id_importance" = "American ID importance",
  "national_attachment" = "National attachment",
  "asian_id_importance" = "Asian ID importance",
  "asian_interests" = "Common Asian interests",
  "dem" = "DEM",
  "gop" = "GOP",
  "female" = "Female",
  "age" = "Age",
  "us_born_cat" = "US born",
  "chinese" = "Chinese",
  "filipino" = "Filipino",
  "indian" = "Indian",
  "japanese" = "Japanese",
  "korean" = "Korean",
  "other_nat" = "Others"
)
```

# Variables 

**Outcome variables**

- `Calling COVID-19 the Chinese virus is racist`: To what extent do you agree with the following statement?: "Calling COVID-19 the Chinese virus is racist." (1-5 scale)

- `Racial linked fate`: To what extent do you agree or disagree with the following statement? "What happens for Asians in this country will have something to do with what happens in your life." (1-5 scale)

- `Ethnic (or national origin) linked fate`: To what extent do you agree or disagree with the following statement? "What happens for [your ethnic] people in this country will have something to do with what happens in your life." (1-5 scale)

**Independent variables**

- `Violence increased against Asians during COVID`: Based on what you've read or heard, do you think violence against Asian Americans in the United States since the coronavirus outbreak has increased, decreased, or stayed the same? (1-3 scale)

- `Experienced racial discrimination during COVID`: Here are a few things that some people in the United States have experienced since the coronavirus outbreak. Please indicate whether any of the following has happened to you since the coronavirus outbreak because of your race or ethnicity. Select all that apply. (Originally five-choice questions. Rescaled as a dummy variable where 1 represents "experienced" and 0 represents "not experienced".)

- `Democracy importance`: How important is it for you to live in a country that is governed democratically? On this scale where 1 means it is "not at all important" and 10 means "absolutely important" what position would you choose? (1-10 scale)

- `Strong leader favorability`: Having a strong leader who does not have to bother with Congress and elections (1-4 scale)
 
- `Democratic political system favorability`: Having a democratic political system (1-4 scale)

- `Army rule favorability`: Having the army rule the country (1-4 scale)

- `China favorability`: Please indicate your feelings toward China. Ratings between 50 and 100 indicate a favorable and warm attitude, while ratings between 0 and 50 indicate an unfavorable attitude. If you have neutral feelings toward China, please rate it at 50. (1-100 scale)

- `China threatening`: How much threat do you think China poses to the United States? Please choose a number between 0 (no threat) and 100 (extreme threat). (1-100 scale)

- `China democratic`: Where would you place China today on this scale? Please choose a number between 0 (not at all democratic) and 100 (completely democratic). (1-100 scale)

- `American ID importance`: How much does being an American have to do with how you feel about yourself? (1-4 scale)

- `National attachment`: If someone said something bad about American people, how strongly would you feel it is as if they said something bad about you? (1-4 scale)

**Confounders**

- `Age`: A continuous variable 

- Party ID dummies: `DEM,` `GOP`

**Confounders / Moderating variables** 

- `Female`: "Female" = 1, "Non-female" = 0

- `US born`: "Born in the U.S." = 1, "Born outside the U.S." = 0

- National origin group dummies: `Chinese,` `Filipino,` `Indian,` `Japanese,` `Korean,` `Others`

```{r sum-table-2, echo = FALSE}
df %>%
  select(china_virus_racist, racial_linked_fate, ethnic_linked_fate, violence_against_asians, racial_covid_dis_cat, democracy_importance, china_fav, china_threat, china_demo, pol_strong_leader, pol_democratic, pol_army_rule, american_id_importance, national_attachment) %>%
  datasummary_skim(table = "Variable summary")
```

# Hypotheses 

## Positive associations 

1. Outcomes ~ Negative covid experience (`Violence increased against Asians during COVID`, `Experienced racial discrimination during COVID`) (**Accepted**)

2. Outcomes ~ Democracry related variables (`Democracy importance`) (**Accepted**) 

- The coefficients for the `Democratic system favorability` variable in Table \@ref(tab:main-chinese) all have positive signs. However, these coefficients are not statistically detectable.

3. Outcomes ~ Positive China variables (`China favorability`, `China democratic`) (Overall, **Not accepted**)

4. Outcomes ~ American ID importance (**Accepted**) 

5. Outcomes ~ National attachment (**Not accepted**) 

## Negative associations 

1. Outcomes ~ Negative China variables (`China threatening`) (**Not accepted**)

- The coefficients for the `China threatening` variable in Table \@ref(tab:main-chinese) all have negative signs. However, they were soon reduced when demographic controls were introduced.

# Main analysis 

In the following Tables \@ref(tab:main-table), all regression coefficients are standardized. OLS models and robust standard errors are applied, and p-values are included inside the parentheses.

* Table \@ref(tab:main-chinese) presents the estimated associations between the "Chinese virus racist" variable and predictors. Since `Democracy importance` and `Democratic system favorability` are conceptually close, I included one at a time. Models 3 and 5 includes `Democracy importance` while model 4 includes `Democratic system favorability.` Model 5 incorporates population weights that were created using the raking method, which was based on the Chinese, Indian, Female, and US-born dummy variables. The target variables were obtained from the 2020 US Census.

Table \@ref(tab:main-table) presents the estimated associations between all five outcome variables and predictors.

```{r, echo = FALSE}
mods_cv <- list(
  "Model 1" = standardize(lm(china_virus_racist ~ violence_asian_cat + racial_covid_dis_cat + democracy_importance, df)),
  "Model 2" = standardize(lm(china_virus_racist ~ democracy_importance + china_fav + china_threat + china_demo, df)),
  "Model 3" = standardize(lm(china_virus_racist ~ violence_asian_cat + racial_covid_dis_cat + democracy_importance + china_fav + china_threat + china_demo + american_id_importance + national_attachment, df)),
  "Model 4" = standardize(lm(china_virus_racist ~ violence_asian_cat + racial_covid_dis_cat + pol_democratic + china_fav + china_threat + china_demo + dem + gop + american_id_importance + national_attachment, df)),
  "Model 5" = standardize(lm(china_virus_racist ~ violence_asian_cat + racial_covid_dis_cat + democracy_importance + china_fav + china_threat + china_demo + female + age + us_born_cat + dem + gop + american_id_importance + national_attachment + chinese, df, weight = weights))
)
```

```{r main-chinese, echo = FALSE}
modelsummary(
  title = "Only the Chinese virus racist",
  mods_cv,
  coef_omit = "Intercept",
  fmt = 2,
  estimate = "{estimate}{stars}",
  statistic = "({p.value})",
  coef_map = cm,
  vcov = "robust",
  output = "markdown"
)
```

```{r, echo = FALSE}
mods <- list(
  "Chinese virus racist" = standardize(lm(china_virus_racist ~ violence_asian_cat + racial_covid_dis_cat + democracy_importance + china_fav + china_threat + china_demo + female + age + us_born_cat + dem + gop + american_id_importance + national_attachment + chinese, df)),
  "Chinese virus racist (weighted)" = standardize(lm(china_virus_racist ~ violence_asian_cat + racial_covid_dis_cat + democracy_importance + china_fav + china_threat + china_demo + female + age + us_born_cat + dem + gop + american_id_importance + national_attachment + chinese, df, weight = weights)),
  "Racial linked fate" = standardize(lm(racial_linked_fate ~ violence_asian_cat + racial_covid_dis_cat + democracy_importance + china_fav + china_threat + china_demo + female + age + us_born_cat + dem + gop + american_id_importance + national_attachment + chinese, df)),
  "Racial linked fate (weighted)" = standardize(lm(racial_linked_fate ~ violence_asian_cat + racial_covid_dis_cat + democracy_importance + china_fav + china_threat + china_demo + female + age + us_born_cat + dem + gop + american_id_importance + national_attachment + chinese, df, weight = weights)),
  "Ethnic linked fate" = standardize(lm(ethnic_linked_fate ~ violence_asian_cat + racial_covid_dis_cat + democracy_importance + china_fav + china_threat + china_demo + female + age + us_born_cat + dem + gop + american_id_importance + national_attachment + chinese, df)),
  "Ethnic linked fate (weighted)" = standardize(lm(ethnic_linked_fate ~ violence_asian_cat + racial_covid_dis_cat + democracy_importance + china_fav + china_threat + china_demo + female + age + us_born_cat + dem + gop + american_id_importance + national_attachment + chinese, df, weight = weights))
)
```

```{r main-table, echo = FALSE}
modelsummary(
  title = "All outcomes",
  mods,
  coef_omit = "Intercept",
  fmt = 2,
  estimate = "{estimate}{stars}",
  statistic = "({p.value})",
  coef_map = cm,
  vcov = "robust",
  output = "markdown"
)
```

# Subgroup analysis

## By gender 

```{r sub-chinese-g, echo = FALSE}
df %>%
  mutate(female = ifelse(female == 1, "Female", "Male")) %>%
  nest_by(female) %>%
  mutate(models = list(standardize(lm(china_virus_racist ~ violence_asian_cat + racial_covid_dis_cat + democracy_importance + china_fav + china_threat + china_demo + age + us_born_cat + dem + gop + american_id_importance + national_attachment, data)))) %>%
  pull(models, name = female) %>%
  modelsummary(
    .,
    title = "Chinese virus racist",
    coef_omit = "Intercept",
    fmt = 2,
    estimate = "{estimate}{stars}",
    statistic = "({p.value})",
    coef_map = cm,
    vcov = "robust",
    output = "markdown"
  )
```

```{r racial-lf-g, echo = FALSE}
df %>%
  mutate(female = ifelse(female == 1, "Female", "Male")) %>%
  nest_by(female) %>%
  mutate(models = list(standardize(lm(racial_linked_fate ~ violence_asian_cat + racial_covid_dis_cat + democracy_importance + china_fav + china_threat + china_demo + age + us_born_cat + dem + gop + american_id_importance + national_attachment, data)))) %>%
  pull(models, name = female) %>%
  modelsummary(
    .,
    title = "Racial linked fate",
    coef_omit = "Intercept",
    fmt = 2,
    estimate = "{estimate}{stars}",
    statistic = "({p.value})",
    coef_map = cm,
    vcov = "robust",
    output = "markdown"
  )
```

```{r ethnic-lf-g, echo = FALSE}
df %>%
  mutate(female = ifelse(female == 1, "Female", "Male")) %>%
  nest_by(female) %>%
  mutate(models = list(standardize(lm(ethnic_linked_fate ~ violence_asian_cat + racial_covid_dis_cat + democracy_importance + china_fav + china_threat + china_demo + age + us_born_cat + dem + gop + american_id_importance + national_attachment + chinese, data)))) %>%
  pull(models, name = female) %>%
  modelsummary(
    .,
    title = "Ethnic linked fate",
    coef_omit = "Intercept",
    fmt = 2,
    estimate = "{estimate}{stars}",
    statistic = "({p.value})",
    coef_map = cm,
    vcov = "robust",
    output = "markdown"
  )
```

## By US born status 

```{r sub-chinese-u, echo = FALSE}
df %>%
  mutate(us_born_cat = ifelse(us_born_cat == 1, "US born", "Foreign born")) %>%
  nest_by(us_born_cat) %>%
  mutate(models = list(standardize(lm(china_virus_racist ~ violence_asian_cat + racial_covid_dis_cat + democracy_importance + china_fav + china_threat + china_demo + age + female + dem + gop + american_id_importance + national_attachment + chinese, data)))) %>%
  pull(models, name = us_born_cat) %>%
  modelsummary(
    .,
    title = "Chinese virus racist",
    coef_omit = "Intercept",
    fmt = 2,
    estimate = "{estimate}{stars}",
    statistic = "({p.value})",
    coef_map = cm,
    vcov = "robust",
    output = "markdown"
  )
```

```{r racial-lf-u, echo = FALSE}
df %>%
  mutate(us_born_cat = ifelse(us_born_cat == 1, "US born", "Foreign born")) %>%
  nest_by(us_born_cat) %>%
  mutate(models = list(standardize(lm(racial_linked_fate ~ violence_asian_cat + racial_covid_dis_cat + democracy_importance + china_fav + china_threat + china_demo + age + female + dem + gop + american_id_importance + national_attachment + chinese, data)))) %>%
  pull(models, name = us_born_cat) %>%
  modelsummary(
    .,
    title = "Racial linked fate",
    coef_omit = "Intercept",
    fmt = 2,
    estimate = "{estimate}{stars}",
    statistic = "({p.value})",
    coef_map = cm,
    vcov = "robust",
    output = "markdown"
  )
```

```{r ethnic-lf-u, echo = FALSE}
df %>%
  mutate(us_born_cat = ifelse(us_born_cat == 1, "US born", "Foreign born")) %>%
  nest_by(us_born_cat) %>%
  mutate(models = list(standardize(lm(ethnic_linked_fate ~ violence_asian_cat + racial_covid_dis_cat + democracy_importance + china_fav + china_threat + china_demo + age + female + dem + gop + american_id_importance + national_attachment + chinese, data)))) %>%
  pull(models, name = us_born_cat) %>%
  modelsummary(
    .,
    title = "Ethnic linked fate",
    coef_omit = "Intercept",
    fmt = 2,
    estimate = "{estimate}{stars}",
    statistic = "({p.value})",
    coef_map = cm,
    vcov = "robust",
    output = "markdown"
  )
```

## By national origin membership

```{r sub-chinese, echo = FALSE}
df %>%
  nest_by(asian_nat) %>%
  mutate(models = list(standardize(lm(china_virus_racist ~ violence_asian_cat + racial_covid_dis_cat + democracy_importance + china_fav + china_threat + china_demo + female + age + us_born_cat + dem + gop + american_id_importance + national_attachment, data)))) %>%
  pull(models, name = asian_nat) %>%
  modelsummary(
    .,
    title = "Chinese virus racist",
    coef_omit = "Intercept",
    fmt = 2,
    estimate = "{estimate}{stars}",
    statistic = "({p.value})",
    coef_map = cm,
    vcov = "robust",
    output = "markdown"
  )
```

```{r racial-lf, echo = FALSE}
df %>%
  nest_by(asian_nat) %>%
  mutate(models = list(standardize(lm(racial_linked_fate ~ violence_asian_cat + racial_covid_dis_cat + democracy_importance + china_fav + china_threat + china_demo + female + age + us_born_cat + dem + gop + american_id_importance + national_attachment, data)))) %>%
  pull(models, name = asian_nat) %>%
  modelsummary(
    .,
    title = "Racial linked fate",
    coef_omit = "Intercept",
    fmt = 2,
    estimate = "{estimate}{stars}",
    statistic = "({p.value})",
    coef_map = cm,
    vcov = "robust",
    output = "markdown"
  )
```

```{r ethnic-lf, echo = FALSE}
df %>%
  nest_by(asian_nat) %>%
  mutate(models = list(standardize(lm(ethnic_linked_fate ~ violence_asian_cat + racial_covid_dis_cat + democracy_importance + china_fav + china_threat + china_demo + female + age + us_born_cat + dem + gop + american_id_importance + national_attachment, data)))) %>%
  pull(models, name = asian_nat) %>%
  modelsummary(
    .,
    title = "Ethnic linked fate",
    coef_omit = "Intercept",
    fmt = 2,
    estimate = "{estimate}{stars}",
    statistic = "({p.value})",
    coef_map = cm,
    vcov = "robust",
    output = "markdown"
  )
```